Using reference models in feature selection problems \vspace{.1in}

### 2019-11-05 paper/ref_approach.tex
revised

\documentclass[american,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in feature selection problems},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{soul}
\usepackage{mathtools}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx,pdflscape}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{supertabular}
%\usepackage{booktabs,caption,fixltx2e}
\usepackage{booktabs,fixltx2e}
\usepackage[font={small,it}]{caption}
\usepackage{tcolorbox}
\usepackage{paralist}
\usepackage{multicol}
\setcitestyle{round}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\theoremstyle{definition}
\newtheorem{example}{Example}
\newcommand{\note}[1]{\textcolor{red}{#1}}

@@

    \author{
    Federico Pavone, 
  Juho Piironen,
  Paul-Christian B\"{u}rkner
  and Aki Vehtari \footnote{Helsinki Institute for Information Technology HIIT,
  Department of Computer Science, Aalto University, Finland.}
  }

@@

In data based approaches, such as Lasso selection
\citep{tibshirani1996regression} or stepwise backward/forward
regression \citep{venables2013modern,harrell2015regression}, the
observed empirical data distribution is utilised as a proxy of future
data usually in combination with cross-validation or information
criteria to provide estimates for out-of-sample predictive
performance.  In contrast, reference model based methods approximate
the future data generation mechanism using the predictive distribution
of a reference model, which can be, for example, a full-encompassing
model including all covariates.  The main assumption under any
reference model approach is that we operate in an
$\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
constructed a model which reflects our beliefs about
the future data in the best possible way and which has passed model checking and criticism
\citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
has been used for a long time in Bayesian statistics since the seminal
work of \citet{paper:reference_lindley}. For more historical
references, see the papers by \citet{vehtari2012survey} and
\citet{paper:model_selection}, and for most recent methodological
development see \citet{paper:projpred}.

@@

To motivate the further discussion and experiments, we start by simple
example comparing projection predictive approach (\emph{projpred},
\citet{paper:projpred}) which uses a reference model and classic
stepwise backward regression (steplm).  using the body fat data
\citep{johnson1996fitting}\footnote{The analysis is based on
  \texttt{R}-notebook by Vehtari available at
  \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.  The
experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
covariates which are anthropometric measurements (e.g., height, weight
and thicknes of skin and fat in different body locations). The
covariates are are highly correlated which causes additional
challenge in the feature selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of fat sufficiently well while requiring least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using \emph{steplm} with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions

For the selection via projpred, the Bayesian reference model includes
all the covariates using a regularised horseshoe prior on the
covariate coefficients \citep{paper:rhs}. Submodels are explored using
forward search (the results are not sensitive to whether forward or
backward search is used), and the predictive utility is the expected
log-predictive density (elpd) estimated using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.  We select the smallest  submodel with an elpd score similar to the reference model
when taking into account the uncertainty in estimating the predictive
model performance. See Appendix A for brief review of projection
predictive approach and \citet{paper:model_selection} and
\citet{paper:projpred} for more details. The complete projpred procedure is implemented in the \texttt{projpred} R package.

@@

A good predictive model is able to filter part of the noise present in
the data. The noise is the main source of the instability and tends to
obscure the relevance of the covariates in relation to the target
variable of interest. Let us consider the following simple
explanatory example taken from \cite{paper:projpred}. The data
generation mechanism is
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
\end{alignat}
where $f$ is the latent variable of interest of which $Y$ is a noisy
observation. The first $k$ covariates are strongly related to the
target variable $Y$ and correlated among themselves. Precisely, $\rho$
is the correlation among any pair of the first $k$ covariates, whereas
$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
any relevant covariate and, respectively, $f$ and $Y$. If we had an
infinite amount of observations, the sample correlation would be equal
to the true correlation between $X_j$ and $Y$. However, even in this
ideal asymptotic regime, this correlation would still remain a biased
indicator of the true relevance of each covariate (represented by the
correlation between $X_j$ and $f$) due to the intrinsic noisy nature
of $Y$.

@@

In the bodyfat example above we desired at the same time good
predictive performance and selection of a smaller number of
features. When the goal is to select a minimal subset of features
which have similar predictive performance as the full model we call it
\emph{minimal subset feature selection}. This minimal subset might
exclude features which have some predictive information about the
target but given the minimal subset, these features are not able to
provide such additional information which would improve predictive
performance. The usual reason for this is that the relevant features
not in the minimal subset highly correlate with features already in
the minimal subset. We will later return to a problem of finding all
the features with some predictive power.

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different size with a relatively large number of
features $p=100$ with with $k=20$ of them being predictive.
We compare the minimal subset feature selection perfomance of
projection predictive approach (with a reference model), a Bayesian
stepwise forward selection (without a reference model), and stepwise
forward selection with and without a reference model.
\begin{itemize}
\item projpred: The Projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation.

\item steplm (data based): Stepwise selection using AIC as in the bodyfat example.

\item steplm (reference model based): The reference model is the same as for
 projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
 are used to replace the target variable $y$. The same AIC selection strategy 
 as in the data based steplm is used.

\item Bayesian stepwise selection (data based): At each step, the fitted model
 is a Bayesian linear regression using the regularised horseshoe
  prior and the feature excluded is the one with the highest Bayesian
  $p$-value defined as:
\begin{equation}
\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}
\end{equation}
The selection continues if the reduced model has an elpd score higher 
(i.e., better) than the current model.

\item Bayesian stepwise selection (reference model based): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$. The same Bayesian
  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.

%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
\end{itemize}

In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR) of the selected submodel,
averaged after 100 data simulations. We see that projpred has superior FDR and the
smallest RMSE. Using a reference model improves steplm significantly,
but the minimal subset feature selection stays unreliable. Stepwise
Bayesian linear regression model without a reference model is better
than steplm without a reference model, but the minimal subset feature
selection is unreliable.

Figure \ref{fig:entropy} reports the entropy scores for the different
methods compared. Lower entropy corresponds to a more stable
selection. Highly correlated predictive features may happen to be
alternately selected, making the measure of the stability of the
selection a non-trivial task. Entropy suffers of such a problem, thus
such a measure should be seen as one of different possible
measurements of the actual stability. 
[TODO: please clarify the above sentences about entropy.] 
The use of a reference model
improves slightly stability of steplm in feature selection. The
projection predictive approach results to be far more stable than all
other approaches. This is likely due to projpred being based on better
decision theoretical formulation which 1) takes into account the full
predictive distribution and not just point estimate and 2) projects
the reference model posterior to the submodel instead of using a
simple refit of submodels.

@@

An alternative to minimal subset feature selection is \emph{complete
  feature selection} in which the goal is to find all relevant
features that have some predictive information about the target. In
complete feature selection it is possible that there are theoretically
relevant features, but given finite noisy data we are not able infer their relevance.
The projection predictive approach was originally designed for the minimal subset
feature selection but we will generalized it for the complete
feature selection case. In addition, we analyse the benefits of the reference
model approach in combination with three other complete feature
selection approaches.

As criteria of selection performance, we evaluate the average false
discovery rate (i.e., the ratio of the number of non-relevant selected
features over the number of selected features) and the average
sensitivity (i.e., the ratio of the number of relevant selected
features over the total number of relevant features). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \cite{paper:stability}.

@@

We can use the projection predictive approach for complete feature
selection by using it iteratively.  Applying the straightforward
implementation of projpred, we are able to select a minimal subset of
features, which yield to a model with a predictive performance
comparable to the full model one.  The iterative projection repeats
the projpred selection for different iterations, at each time
excluding from the search the features selected in the previous
iterations. At each iteration the selected submodel size corresponds to the
one having a predictive performance close enough to the baseline
model, which in this iterative version is the submodel with the
highest predictive score explored at the current iteration. The
stopping rule that we adopted is the following:
\begin{equation} 
\label{eq:rule_of_thumb}
\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
\end{equation}
where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
the stopping rule.
The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
number of observations or not very predictive features. 
In our experiments we chose the default value used in the \texttt{projpred} 
\texttt{R}-package that corresponds to $\alpha=0.16$.
\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
I did in the thesis}
TODO: add the pseudo code here

@@

% For the Bayesian regression
% models with these priors, we compare the posterior shrinkage and the
% correct estimation of the sparse signals with and without using a
% reference model as a noise filter. For this purpose, we consider the
% average SSE (sum of square errors) and the average SESE (sum of
% expected square errors) as quantities measuring estimation
% accuracy. They are defined as \
% \begin{align}
% \text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}], \label{eq:SESE}
% \end{align}
% where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
% $\hat{\theta}_{j}$ is the posterior median of each parameter
% $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
% independent of the number of statistical units.  The SESE takes the
% posterior uncertainty in account and thus also the shrinkage of the
% posterior distributions, whereas the SSE only measures the bias in the
% point estimates.  Any (sensible) point estimate could be used to
% compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
% use the posterior median. The results that we show later on in Section
% \ref{shrinkage-signal} are not sensitive to the choice of this point
% estimate.

% For shrinkage priors, one central aspect is the amount of shrinkage
% they actually impose on the relevant and irrelevant features. Ideally,
% the irrelevant features should be completely shrunk to zero while the
% relevant features should not be shrunk at all. The amount of shrinkage
% can be quantified by the shrinkage factor $\kappa_{j}$ for each
% parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
% (complete shrinkage). For model \eqref{eq:normal_means_problem2} with
% a hierarchical shrinkage prior of the type
% \begin{align}
% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
% &\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
% \end{align}
% the shrinkage factor $\kappa_{j}$ is defined as
% \begin{equation}
% \kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
% \end{equation}
% \
% For RHS and DL priors we have
% \begin{equation}
% \kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
% \end{equation}
% In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
% the global and local shrinkage parameters of the regularised horseshoe
% prior \cite[for further details see][]{paper:rhs}, whereas on the
% right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
% the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
% notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
% of $\kappa_{j}$ as a point estimate.

@@

%\appendix

@@

>>>>

\documentclass[a4]{article}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in feature selection problems},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\textwidth 6.0 true in
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{soul}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{graphicx,pdflscape}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{supertabular}
%\usepackage{booktabs,caption,fixltx2e}
\usepackage{booktabs,fixltx2e}
\usepackage[font={small,it}]{caption}
\usepackage{tcolorbox}
\usepackage{paralist}
\usepackage{multicol}
\setcitestyle{round}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\theoremstyle{definition}
\newtheorem{example}{Example}
\DeclareMathOperator{\Cor}{Cor}
\DeclareMathOperator{\N}{N}
\newcommand{\note}[1]{\textcolor{red}{#1}}

@@

    \author{
    Federico Pavone, 
  Juho Piironen,
  Paul-Christian B\"{u}rkner
  and Aki Vehtari \footnote{Department of Computer Science, Aalto University, Finland.}
  }

@@

In data based approaches, such as Lasso selection
\citep{tibshirani1996regression} or stepwise backward/forward
regression \citep{venables2013modern,harrell2015regression}, the
observed empirical data distribution is utilised as a proxy of future
data usually in combination with cross-validation or information
criteria to provide estimates for out-of-sample predictive
performance.  In contrast, reference model based methods approximate
the future data generation mechanism using the predictive distribution
of a reference model, which can be, for example, a full-encompassing
model including all covariates.  The main assumption under any
reference model approach is that we operate in an
$\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
constructed a model which reflects our beliefs about
the future data in the best possible way and which has passed model checking and criticism
\citep[see, e.g.][]{gelman2013bayesian,gabry2019visualization}.  The reference model approach
has been used in Bayesian statistics at least since the seminal
work of \citet{paper:reference_lindley}. For more historical
references, see the papers by \citet{vehtari2012survey} and
\citet{paper:model_selection}, and for most recent methodological
development see \citet{paper:projpred}.

@@

To motivate the further discussion and experiments, we start by simple
variable selection example using body fat data by \citet{johnson1996fitting}.
We compare projection predictive approach (\emph{projpred},
\citet{paper:projpred}) which uses a reference model, and classic
stepwise backward regression (steplm).
% \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
%   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
The experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
covariates which are anthropometric measurements (e.g., height, weight
and thicknes of skin and fat in different body locations). The
covariates are are highly correlated which causes additional
challenge in the feature selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of fat well while requiring least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using \emph{steplm} with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions.

For the selection via projpred, the Bayesian reference model includes
all the covariates using a regularised horseshoe prior~\citep{paper:rhs} on the
covariate coefficients. Submodels are explored using
forward search (the results are not sensitive to whether forward or
backward search is used), and the predictive utility is the expected
log-predictive density (elpd) estimated using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.  We select the smallest  submodel with an elpd score similar to the reference model
when taking into account the uncertainty in estimating the predictive
model performance. See Appendix A for brief review of projection
predictive approach and \citet{paper:model_selection} and
\citet{paper:projpred} for more details. The complete projpred procedure is implemented in the \texttt{projpred} R package.

@@

A good predictive model is able to filter part of the noise present in
the data. The noise is the main source of the instability and tends to
obscure the relevance of the covariates in relation to the target
variable of interest. Let us consider the following simple
explanatory example taken from \cite{paper:projpred}. The data
generation mechanism is
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim \N(0,1) && \nonumber \\ 
     Y|&f\sim \N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} \N(\sqrt{\rho}f,1-\rho) \quad &&j=1,\ldots,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} \N(0,1) &&j=k+1,\ldots,p \nonumber,
\end{alignat}
where $f$ is the latent variable of interest of which $Y$ is a noisy
observation. The first $k$ covariates are strongly related to the
target variable $Y$ and correlated among themselves. Precisely, $\rho$
is the correlation among any pair of the first $k$ covariates, whereas
$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
any relevant covariate and, respectively, $f$ and $Y$. If we had an
infinite amount of observations, the sample correlation would be equal
to the true correlation between $X_j$ and $Y$. However, even in this
ideal asymptotic regime, this correlation would still remain a biased
indicator of the true relevance of each covariate (represented by the
correlation between $X_j$ and $f$) due to the intrinsic noisy nature
of $Y$.

@@

In the bodyfat example above, we desired at the same time good
predictive performance and selection of a smaller number of
features. When the goal is to select a minimal subset of features,
which have similar predictive performance as the full model, we call it
\emph{minimal subset feature selection}. This minimal subset might
exclude features which have some predictive information about the
target, but given the minimal subset these features are not able to
provide such additional information that would improve predictive
performance. The usual reason for this is that the relevant features
not in the minimal are subset highly correlated with features already in
the minimal subset. We will return to a problem of finding all
the features with some predictive power in Section~\ref{complete-selection}.

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different sizes with a relatively large number
of features $p=100$ with $k=20$ of them being predictive.  We compare
the minimal subset feature selection perfomance of projection
predictive approach (with a reference model), a Bayesian stepwise
forward selection with and without a reference model, and maximum
likelihood stepwise forward selection with and without a reference
model:
\begin{itemize}
\item projpred: The projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components \citep{piironen2018} as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation.

\item Bayesian stepwise selection (without a reference model): At each step, the fitted model
 is a Bayesian linear regression using the regularised horseshoe
  prior and the feature excluded is the one with the highest Bayesian
  $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$.
The selection continues if the reduced model has an elpd score higher 
(i.e., better) than the current model.

\item Bayesian stepwise selection (with a reference model): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$. The same Bayesian
  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.

%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
\item steplm (without a reference model): Stepwise selection using AIC as in the bodyfat example.

\item steplm (with a reference model): The reference model is the same as for
 projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
 are used to replace the target variable $y$. The same AIC selection strategy 
 as in the data based steplm is used.

\end{itemize}

In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR, the ratio of the number of non-relevant selected
features over the number of selected features) of the selected submodel,
averaged after 100 data simulations. We see that projpred has superior FDR and the
smallest RMSE. Using a reference model improves steplm significantly,
but the minimal subset feature selection stays unreliable. Stepwise
Bayesian linear regression model without a reference model is better
than steplm without a reference model, but the minimal subset feature
selection is unreliable.

When the variable selection is repeated with different simulated data
sets, there is some variability in which variables are selected. We
measure the stability of variable selection by computing the entropy
of observed distribution over different models. The smallest entropy
would be obtained if the approach selectes always the same set of
variables, and the largest entropy would be observed if the approach
would always select different set of variables.
Figure \ref{fig:entropy} reports the entropy scores for the different
methods compared.  
The use of a reference model
improves slightly the stability of steplm in feature selection. The
projection predictive approach results to be far more stable than all
other approaches. This is likely due to projpred being based on better
decision theoretical formulation which 1) takes into account the full
predictive distribution and not just point estimate and 2) projects
the reference model posterior to the submodel instead of using a
simple refit of submodels.

@@

An alternative to minimal subset feature selection is \emph{complete
  feature selection} in which the goal is to find all relevant
features that have some predictive information about the target. In
complete feature selection, it is possible that there are theoretically
relevant features, but given finite noisy data we are not able infer their relevance.
The projection predictive approach was originally designed for the minimal subset
feature selection, but we generalize it here for the complete
feature selection case. In addition, we analyse the benefits of the reference
model approach in combination with three other complete feature
selection approaches.

As criteria of selection performance, we evaluate the average false
discovery rate and the average
sensitivity (i.e., the ratio of the number of relevant selected
features over the total number of relevant features). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \citet{paper:stability}.

@@

We can use the projection predictive approach for complete feature
selection by using it iteratively.  Applying the straightforward
implementation of projpred, we are able to select a minimal subset of
features, which yield to a model with a predictive performance
comparable to the full model one.  The iterative projection repeats
the projpred selection for different iterations, at each time
excluding from the search the features selected in the previous
iterations. At each iteration the selected submodel size corresponds to the
one having a predictive performance close enough to the baseline
model, which in this iterative version is the submodel with the
highest predictive score explored at the current iteration. The
stopping rule that we adopted is the following:
\begin{equation} 
\label{eq:rule_of_thumb}
\text{min} \{i\in \{0,\ldots,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \},
\end{equation}
where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
the stopping rule.
The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
number of observations or not very predictive features. 
In our experiments we chose the default value used in the \texttt{projpred} 
\texttt{R}-package that corresponds to $\alpha=0.16$.
\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
I did in the thesis}
TODO: add the pseudo code here

@@

% For the Bayesian regression
% models with these priors, we compare the posterior shrinkage and the
% correct estimation of the sparse signals with and without using a
% reference model as a noise filter. For this purpose, we consider the
% average SSE (sum of square errors) and the average SESE (sum of
% expected square errors) as quantities measuring estimation
% accuracy. They are defined as \
% \begin{align}
% \text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},\ldots,z_{p})d\theta_{j} \\
% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},\ldots,z_{p}], \label{eq:SESE}
% \end{align}
% where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
% $\hat{\theta}_{j}$ is the posterior median of each parameter
% $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
% independent of the number of statistical units.  The SESE takes the
% posterior uncertainty in account and thus also the shrinkage of the
% posterior distributions, whereas the SSE only measures the bias in the
% point estimates.  Any (sensible) point estimate could be used to
% compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
% use the posterior median. The results that we show later on in Section
% \ref{shrinkage-signal} are not sensitive to the choice of this point
% estimate.

% For shrinkage priors, one central aspect is the amount of shrinkage
% they actually impose on the relevant and irrelevant features. Ideally,
% the irrelevant features should be completely shrunk to zero while the
% relevant features should not be shrunk at all. The amount of shrinkage
% can be quantified by the shrinkage factor $\kappa_{j}$ for each
% parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
% (complete shrinkage). For model \eqref{eq:normal_means_problem2} with
% a hierarchical shrinkage prior of the type
% \begin{align}
% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,\ldots,p \\
% &\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
% \end{align}
% the shrinkage factor $\kappa_{j}$ is defined as
% \begin{equation}
% \kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
% \end{equation}
% \
% For RHS and DL priors we have
% \begin{equation}
% \kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
% \end{equation}
% In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
% the global and local shrinkage parameters of the regularised horseshoe
% prior \cite[for further details see][]{paper:rhs}, whereas on the
% right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
% the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
% notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
% of $\kappa_{j}$ as a point estimate.

@@

\appendix

@@

\section*{Appendix}
